Instruction

### 2018-12-26 script/Rmd/instruction.Rmd
Delete pdf and create html

---
output:
  html_document: default
  pdf_document: default
  word_document: default
---

---
title: "Instruction"
author: "Atsuko Tominaga"
date: "03/12/2018"
output:
  pdf_document:
fontsize: 12pt
---

@@

@@

```{r 01, out.width = '50%'}
knitr::include_graphics("01.png")
```
```{r 02, out.width = '80%'}
knitr::include_graphics("02.png")
```

@@

```{r 03, out.width = '80%'}
knitr::include_graphics("03.png")
```

@@

```{r mainPatch, out.width = '100%'}
knitr::include_graphics("mainPatch_screen.png")
```

@@

```{r inst_g1, out.width = '80%'}
knitr::include_graphics("inst_g1.png")
```

@@

```{r stim_n, out.width = '80%'}
knitr::include_graphics("stim_n.png")
```

@@

```{r inst_g2, out.width = '80%'}
knitr::include_graphics("inst_g2.png")
```

@@

#### 1) Teaching condition
##### 1st Stimulus

@@

```{r stim_a, out.width = '80%', fig.cap = 'Articulation'}
knitr::include_graphics("stim_a.png")
```

@@

```{r inst_t, out.width = '80%'}
knitr::include_graphics("inst_t.png")
```

@@

##### 2nd Stimulus

@@

```{r stim_d, out.width = '80%', fig.cap = 'Dynamics'}
knitr::include_graphics("stim_d.png")
```

@@

#####  3rd Stimulus

@@

```{r stim_t, out.width = '80%', fig.cap = 'Tempo Change'}
knitr::include_graphics("stim_t.png")
```

@@

#### 2) Performing condition
##### 1st Stimulus

@@

```{r inst_p, out.width = '80%'}
knitr::include_graphics("inst_p.png")
```

>>>>

---
output:
  html_document: default
---

---
title: "Instruction"
author: "Atsuko Tominaga"
date: "26/12/2018"
output:
  html_document:
    css: style.css
---

@@

<style type="text/css">
/* Whole document: */
body{
  font-family: Helvetica;
  font-size: 14pt;
}
<!-- /* Headers */ -->
<!-- h1,h2,h3,h4,h5,h6{ -->
<!--   font-size: 24pt; -->
<!-- } -->
</style>

@@

![](01.png){ width=50% }
![](02.png){ width=80% }

@@

![](03.png){ width=80% }

@@

![](mainPatch_screen.png)

@@

![](inst_g1.png){ width=80% }

@@

![](stim_n.png){ width=80% }

@@

![](inst_g2.png){ width=80% }

@@

#### 1) Teaching condition
> 1st Stimulus

@@

![](stim_a.png){ width=80% }

@@

![](inst_t.png){ width=80% }

@@

> 2nd Stimulus

@@

![](stim_d.png){ width=80% }

@@

> 3rd Stimulus

@@

![](stim_t.png){ width=80% }

@@

#### 2) Performing condition
> 1st Stimulus

@@

![](inst_p.png){ width=80% }
